---
title: "Week2Assignment"
author: "Sumit"
date: "June 4, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1. Loading and preprocessing the data

###  **Upload Data** in data MAtrix


```{r}
activity<-read.csv("./repdata_data_activity/activity.csv")
```

### **Process Data** : *Clean data with no NAs*

```{r echo=TRUE}
activity$date<-as.Date(as.character(activity$date))
baseNA<-is.na(activity$steps)
cleandata<-activity[!baseNA,]
```


## 2. What is mean total number of steps taken per day?


###Calculate the total number of steps taken per day

```{r echo=TRUE}
StepsPerDay<-aggregate(cleandata$steps,by=list(cleandata$date),sum)
names(StepsPerDay)[1]<-"Date"
names(StepsPerDay)[2]<-"Steps"
head(StepsPerDay)
```

### Make a histogram of the total number of steps taken each day

```{r echo=TRUE}
hist(StepsPerDay$Steps, xlab = "Total Steps", ylab =" No. of Days" , main="Histogram of Total Steps by day", breaks = 20)
```

###Calculate and report the mean and median of the total number of steps taken per day

```{r echo=TRUE}
mean(StepsPerDay$Steps)
median(StepsPerDay$Steps)
```

## 3. What is the average daily activity pattern

###Time Series Plot

```{r echo=TRUE}
library(ggplot2)
StepsPerInterval<-aggregate(cleandata$steps,by=list(cleandata$interval),mean)
names(StepsPerInterval)[1]<-"Interval"
names(StepsPerInterval)[2]<-"Steps"
qplot(Interval , Steps, data = StepsPerInterval, xlab ="Average steps ", ylab="interval",geom ="line")
```


### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps
```{r echo=TRUE}
StepsPerInterval[which(StepsPerInterval$Steps== max(StepsPerInterval$Steps)),]
```

##4. Imputing missing values

### Calculate and report the total number of missing values in the dataset

```{r echo=TRUE}
sum(is.na(activity$steps))
```

###2.Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.


